### 2018-10-10 paper/paper.tex
update paper

% Block of authors and their affiliations starts here:
% NOTE: Authors with same affiliation, if the order of authors allows,
%   should be entered in ONE field, separated by a comma.
%   \EMAIL field can be repeated if more than one author
\ARTICLEAUTHORS{%
  \AUTHOR{Manuel Schneckenreither% \orcidID{0000-0002-4812-4665}
  }
  \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
  \EMAIL{manuel.schneckenreither@uibk.ac.at}} %, \URL{}}

  \AUTHOR{Stefan Haeussler % \orcidID{0000-0003-2589-1367}
  }
  \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
  \EMAIL{stefan.haeussler@uibk.ac.at}}
} % end of the block

@@

In practise the available demand data is used to infer the function $\dmean$ and the value for
$\sigma$. This could be done using regression and statistical analyses. Therefore, in hereafter
these values are expected to be known.

@@

  Let $p \in \Nat$ be the periods. Suppose, the deviations of the mean demand are drawn by $\X_{0}$,
  $\X_{1}$ and the corresponding release pattern follow the random variables $\Lambda_{0}$ and
  $\Lambda_{1}$ respectively.
  % and the standard deviation $\stddev$ over a set of discrete
  Then, if $\stddev(\X_{1}) > \stddev(\X_{0})$  then $\stddev(\Lambda_{1}) > \stddev(\Lambda_{0})$
  is sensible.
  %
  Informally this means that for higher standard deviation in the demand a higher standard deviation
  in the release pattern is sensible.

@@

\begin{definition}
  We define the \emph{\mddname{}} $\mdd{p}$ of period $p$ and the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \mdd{p} \defsym 1 +
    \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}  +
    \frac{\max \{|f(i)-f(i+1)|\ \mid \ \forall 0 \leqslant i \leqslant p \}}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}
  \end{align*}
  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
  $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate
\end{definition}

@@

Intuitively the \mddname{} is a measure of variability and shift of the mean in the demand stream
with respect to the average mean demand and equipped with a lower-bound of $1$. We use the
\mddname{} to average the number of releases and \WIP{}-levels to be able to investigate their
\textsl{\mddname{}}-average slopes over time.

% Maybe here an example?

However,

This time factor

>>>>

% Block of authors and their affiliations starts here:
% NOTE: Authors with same affiliation, if the order of authors allows,
%   should be entered in ONE field, separated by a comma.
%   \EMAIL field can be repeated if more than one author
\ARTICLEAUTHORS{%
  \AUTHOR{Manuel Schneckenreither%
    % \orcidID{0000-0002-4812-4665}
    % , Stefan Haeussler
    % \orcidID{0000-0003-2589-1367}
  }
  \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
    \EMAIL{manuel.schneckenreither@uibk.ac.at}
    \EMAIL{stefan.haeussler@uibk.ac.at}
  } %, \URL{}}

  % \AUTHOR{Stefan Haeussler % \orcidID{0000-0003-2589-1367}
  % }
  % \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
  % \EMAIL{stefan.haeussler@uibk.ac.at}}
} % end of the block

@@

In practise the available demand data is used to infer the function $\dmean$ and the value for
$\sigma$. This is done using regression and other statistical analyses. Therefore, hereafter the
function $\dmean$ and the value for $\sigma$ % these values
are expected to be known. In the following we will use these values to infer important time
information for the analysis of the \LTS{}.

@@

  Let $p \in \Nat$ be the periods. Consider two demand streams where the deviations of the mean
  demand are drawn by $\X_{0}$, $\X_{1}$ and the corresponding release pattern follow the random
  variables $\Lambda_{0}$ and $\Lambda_{1}$ respectively.
  % and the standard deviation $\stddev$ over a set of discrete
  Then, if $\stddev(\X_{1}) > \stddev(\X_{0})$  then $\stddev(\Lambda_{1}) > \stddev(\Lambda_{0})$
  is sensible.
  %
  Informally this means that for higher standard deviation in the demand a higher standard deviation
  in the release pattern is sensible.

@@

\begin{definition}
  We define the \emph{\mddname{}} $\mdd{p}$ of period $p$ and the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \mdd{p} \defsym 1 +
    \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}  +
    \frac{\max \{|f(i)-f(i+1)|\ \mid \ \forall 0 \leqslant i \leqslant p \}}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}
  \end{align*}
  \MS{maybe use moving average for mean. Imagine a demand jump from bottom to top and vice versa! should
    be equal? }
  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
  $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate
\end{definition}

@@

Intuitively the \mddname{} is a measure of variability and maximum leap of the mean in the demand
stream with respect to the average mean demand and equipped with a lower-bound of $1$. We use the
\mddname{} to average the number of releases and \WIP{}-levels to be able to investigate their
\textsl{\mddname{}}-average slopes.

% Maybe here an example?
We compare these slopes to the slopes from the past. The amount of time which is looked into the
past is defined by the defined by the length of the season.
